---
title: "Rating and exploration time"
output: 
  html_document:
    fig_caption: yes
    highlight: default
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: true

  pdf_document:
    toc: yes
    toc_depth: 5
    number_sections: no
    highlight: tango
    latex_engine: xelatex
    fontsize: 12pt
---

\setmainfont{Noto Sans}
\setmathfont{Fira Code}
\colorlet{shadecolor}{gray!10}

<style>
body {
  font-size: 15px;
}

p.caption {
  font-weight: 500;
  font-style: italic;
}

code.r {
  font-family: Consolas, Monaco, monospace;
  font-size: 12px;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "html", cache=TRUE) # "latex" for PDF; "html" for html 
```

```{r load libraries}
library(data.table); library(ggplot2); library(nlme)
```

```{r load the data}
load("../PilotData/IndividualData.RData")
load("../PilotData/ExcludedSubjectList.RData")
```

```{r remove excluded participants}
outside.hit.rate.per.room <- outside.hit.rate.per.room[! SubjectNo %in% excluded.ps]
```
# Correlations between *Curiosity*, *Interest* and *Surprise* scores
## Correlation between *Curiosity* and *Interest*
```{r}
base.cur <- lme(Curiosity ~ 1, random = ~ 1|SubjectNo, data = outside.hit.rate.per.room, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)
cur.int    <- update(base.cur, .~. + Interest, random = ~ 1 + Interest|SubjectNo)
```

```{r}
anova(base.cur, cur.int)
```

## Correlation between *Curiosity* and *Surprise*
```{r}
cur.sur <- update(base.cur, .~. + Surprise, random = ~ 1 + Surprise|SubjectNo)
anova(base.cur, cur.sur)
```

## Correlation between *Interest* and *Surprise*
```{r}
base.int <- lme(Interest ~ 1, random = ~ 1|SubjectNo, data = outside.hit.rate.per.room, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)
int.sur      <- update(base.int, .~. + Surprise, random = ~ 1 + Surprise|SubjectNo)
anova(base.int, int.sur)
```

> So all the three scores correlate with each other.

# Relationships between scores and exploration time
## Relationship between *Curiosity* rating and exploration time
```{r}
baseline      <- lme(InsideDuration ~ 1, random = ~ 1|SubjectNo, data = outside.hit.rate.per.room, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)
cur.model.int <- update(baseline, .~. + Curiosity)
cur.model.slp <- update(cur.model.int, random = ~ 1 + Curiosity|SubjectNo)
```

```{r}
anova(baseline, cur.model.int, cur.model.slp)
```

```{r}
summary(cur.model.slp)
```

## Relationship between *Interest* rating and exploration time
```{r}
int.model.int <- update(baseline, .~. + Interest)
int.model.slp <- update(int.model.int, random = ~ 1 + Interest|SubjectNo)
```

```{r}
anova(baseline, int.model.int, int.model.slp)
```

```{r}
summary(int.model.slp)
```

## Relationship between *Surprise* rating and exploration time
```{r}
sur.model.int <- update(baseline, .~. + Surprise)
sur.model.slp <- update(sur.model.int, random = ~ 1 + Surprise|SubjectNo)
```

```{r}
anova(baseline, sur.model.int, sur.model.slp)
```

```{r}
summary(sur.model.slp)
```

# Find the relative contribution of each score
## Order 1
*Curiosity* -> *Interest* 

```{r}
cur.int.int <- update(cur.model.slp, .~. + Interest)
cur.int.slp <- update(cur.int.int, random = ~ 1 + Curiosity + Interest|SubjectNo)
anova(cur.model.slp, cur.int.int, cur.int.slp)
```

## Order 2
*Curiosity* -> *Surprise* 
```{r}
cur.sur.int <- update(cur.model.slp, .~. + Surprise)
cur.sur.slp <- update(cur.sur.int, random = ~ 1 + Curiosity + Surprise|SubjectNo)
anova(cur.model.slp, cur.sur.int, cur.sur.slp)
```

## Order 3
*Interest* -> *Curiosity* 
```{r}
int.cur.int <- update(int.model.slp, .~. + Curiosity)
int.cur.slp <- update(int.cur.int, random = ~ 1 + Curiosity + Interest|SubjectNo)
anova(int.model.slp, int.cur.int, int.cur.slp)
```

## Order 4
*Interest* -> *Surprise* 
```{r}
int.sur.int <- update(int.model.slp, .~. + Surprise)
int.sur.slp <- update(int.sur.int, random = ~ 1 + Surprise + Interest|SubjectNo)
anova(int.model.slp, int.sur.int, int.sur.slp)
```

## Order 5
*Surprise* -> *Interest* 
```{r}
sur.int.int <- update(sur.model.slp, .~. + Interest)
sur.int.slp <- update(sur.int.int, random = ~ 1 + Surprise + Interest|SubjectNo)
anova(sur.model.slp, sur.int.int, sur.int.slp)
```

## Order 6
*Surprise* -> *Curiosity* 
```{r}
sur.cur.int <- update(sur.model.slp, .~. + Curiosity)
sur.cur.slp <- update(sur.cur.int, random = ~ 1 + Surprise + Curiosity|SubjectNo)
anova(sur.model.slp, sur.cur.int, sur.cur.slp)
```


