---
title: "Comparing the groups"
output: 
  pdf_document:
    toc: yes
    toc_depth: 5
    number_sections: no
    highlight: tango
    latex_engine: xelatex
  fontsize: 12pt
---

\setmainfont{Noto Sans}
\setmathfont{Fira Code}
\colorlet{shadecolor}{gray!10}

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "latex", cache=TRUE) # "latex" for PDF; "html" for html 
```

```{r}
library(data.table); library(ez)
```

```{r load the data}
load("../PilotData/IndividualData.RData")
load("../PilotData/ExcludedSubjectList.RData")
```

```{r remove excluded participants}
outside.hit.rate.item.curiosity.median <- outside.hit.rate.item.curiosity.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.interest.median  <- outside.hit.rate.item.interest.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.surprise.median  <- outside.hit.rate.item.surprise.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.preint.median    <- outside.hit.rate.item.preint.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.presur.median    <- outside.hit.rate.item.presur.median[! SubjectNo %in% excluded.ps]

outside.hit.rate.item.order.curiosity.median <- outside.hit.rate.item.order.curiosity.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.order.interest.median  <- outside.hit.rate.item.order.interest.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.order.surprise.median  <- outside.hit.rate.item.order.surprise.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.order.preint.median    <- outside.hit.rate.item.order.preint.median[! SubjectNo %in% excluded.ps]
outside.hit.rate.item.order.presur.median    <- outside.hit.rate.item.order.presur.median[! SubjectNo %in% excluded.ps]
```

# Compare the *Curiosity* groups
```{r}
outside.hit.rate.item.curiosity.median[,. (Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(CurGrpMd)]
```

**Statistic difference**
```{r}
t.test(SAcc ~ CurGrpMd, outside.hit.rate.item.curiosity.median, paired = T)
```

## Include the item order
```{r}
outside.hit.rate.item.order.curiosity.median[, .(Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(CurGrpMd, ObjOrdGrp)]
```

**Statistic difference**
```{r}
ezANOVA(outside.hit.rate.item.order.curiosity.median, dv = .(SAcc), wid = .(SubjectNo), within = .(CurGrpMd, ObjOrdGrp), type = 3)
```

# Compare the *Interest* groups
```{r}
outside.hit.rate.item.interest.median[,. (Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(IntGrpMd)]
```

**Statistic difference**
```{r}
t.test(SAcc ~ IntGrpMd, outside.hit.rate.item.interest.median, paired = T)
```

## Include the item order
```{r}
outside.hit.rate.item.order.interest.median[, .(Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(IntGrpMd, ObjOrdGrp)]
```

**Statistic difference**
```{r}
ezANOVA(outside.hit.rate.item.order.interest.median, dv = .(SAcc), wid = .(SubjectNo), within = .(IntGrpMd, ObjOrdGrp), type = 3)
```

# Compare the *Surprise* groups
```{r}
outside.hit.rate.item.surprise.median[,. (Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(SurGrpMd)]
```

**Statistic difference**
```{r}
t.test(SAcc ~ SurGrpMd, outside.hit.rate.item.surprise.median, paired = T)
```

## Include the item order
```{r}
outside.hit.rate.item.order.surprise.median[, .(Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(SurGrpMd, ObjOrdGrp)]
```

**Statistic difference**
```{r}
ezANOVA(outside.hit.rate.item.order.surprise.median, dv = .(SAcc), wid = .(SubjectNo), within = .(SurGrpMd, ObjOrdGrp), type = 3)
```


# Compare the *Pre-Interest* groups
```{r}
outside.hit.rate.item.preint.median[,. (Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(PreIntGrpMd)]
```

**Statistic difference**
```{r}
t.test(SAcc ~ PreIntGrpMd, outside.hit.rate.item.preint.median, paired = T)
```

## Include the item order
```{r}
outside.hit.rate.item.order.preint.median[, .(Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(PreIntGrpMd, ObjOrdGrp)]
```

**Statistic difference**
```{r}
ezANOVA(outside.hit.rate.item.order.preint.median, dv = .(SAcc), wid = .(SubjectNo), within = .(PreIntGrpMd, ObjOrdGrp), type = 3)
```

# Compare the *Pre-Surprise* groups
```{r}
outside.hit.rate.item.presur.median[SubjectNo != "P06",. (Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(PreSurGrpMd)]
```

**Statistic difference**
```{r}
t.test(SAcc ~ PreSurGrpMd, outside.hit.rate.item.presur.median[SubjectNo != "P06"], paired = T)
```

## Include the item order
```{r}
outside.hit.rate.item.order.presur.median[SubjectNo != "P06", .(Mean = mean(SAcc, na.rm = T), SD = sd(SAcc, na.rm = T)), by = .(PreSurGrpMd, ObjOrdGrp)]
```

**Statistic difference**
```{r}
ezANOVA(outside.hit.rate.item.order.presur.median[SubjectNo != "P06"], dv = .(SAcc), wid = .(SubjectNo), within = .(PreSurGrpMd, ObjOrdGrp), type = 3)
```






