---
title: "Traits"
output:
  html_notebook:
    fig_caption: yes
    highlight: tango
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 6
    toc_float: yes
    code_folding: hide
  html_document:
    fig_caption: yes
    highlight: tango
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 6
    toc_float: yes
    code_folding: hide
    
---
<style>
body {
  <!-- font-size: 15px; -->
  line-height: 2;
}

h1, h2, h3, h4, h5, h6 {
  color: #158CBA;
}

mark {
  background-color:#FFEB94;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "html", cache=TRUE) # "latex" for PDF; "html" for html
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(data.table); library(ggplot2); library(nlme); library(ez); library(multcomp); library(psychReport); library(psych); library(cowplot); library(RColorBrewer); library(dplyr); library(Rmisc)
```

```{r}
load("./PilotData/IndividualData.RData")
load("./PilotData/ExcludedSubjectList.RData")
```

```{r}
individual.average.data <- individual.average.data[! SubjectNo %in% excluded.ps]
```

# Trait and curiosity 
## PC and EC
```{r}
PC_rating <- with(individual.average.data, cor.test(MeanCur, PC))
EC_rating <- with(individual.average.data, cor.test(MeanCur, EC))
```

## Subscales
```{r}
PCd_rating <- with(individual.average.data, cor.test(MeanCur, PCd))
PCs_rating <- with(individual.average.data, cor.test(MeanCur, PCs))
ECi_rating <- with(individual.average.data, cor.test(MeanCur, ECi))
ECd_rating <- with(individual.average.data, cor.test(MeanCur, ECd))
```

# Trait and recollection accuracy
## PC and EC
```{r}
PC_RAcc <- with(individual.average.data, cor.test(MRAcc, PC))
EC_RAcc <- with(individual.average.data, cor.test(MRAcc, EC))
```

## Subscales
```{r}
PCd_RAcc <- with(individual.average.data, cor.test(MRAcc, PCd))
PCs_RAcc <- with(individual.average.data, cor.test(MRAcc, PCs))
ECi_RAcc <- with(individual.average.data, cor.test(MRAcc, ECi))
ECd_RAcc <- with(individual.average.data, cor.test(MRAcc, ECd))
```

# Summary
|Subscale Score|Curiosity Rating|Recollection Accuracy|
|---|---|---|
|PC|*r* = `r round(PC_rating$estimate[[1]], 2)`, t = `r round(PC_rating$statistic[[1]], 2)`, *p* = `r round(PC_rating$p.value, 2)`|*r* = `r round(PC_RAcc$estimate[[1]], 2)`, t = `r round(PC_RAcc$statistic[[1]], 2)`, *p* = `r round(PC_RAcc$p.value, 2)`|
|EC|*r* = `r round(EC_rating$estimate[[1]], 2)`, t = `r round(EC_rating$statistic[[1]], 2)`, *p* = `r round(EC_rating$p.value, 2)`|*r* = `r round(EC_RAcc$estimate[[1]], 2)`, t = `r round(EC_RAcc$statistic[[1]], 2)`, *p* = `r round(EC_RAcc$p.value, 2)`|
|PC/D|*r* = `r round(PCd_rating$estimate[[1]], 2)`, t = `r round(PCd_rating$statistic[[1]], 2)`, *p* = `r round(PCd_rating$p.value, 2)`|*r* = `r round(PCd_RAcc$estimate[[1]], 2)`, t = `r round(PCd_RAcc$statistic[[1]], 2)`, *p* = `r round(PCd_RAcc$p.value, 2)`|
|PC/S|*r* = `r round(PCs_rating$estimate[[1]], 2)`, t = `r round(PCs_rating$statistic[[1]], 2)`, *p* = `r round(PCs_rating$p.value, 2)`|*r* = `r round(PCs_RAcc$estimate[[1]], 2)`, t = `r round(PCs_RAcc$statistic[[1]], 2)`, *p* = `r round(PCs_RAcc$p.value, 2)`|
|EC/I|*r* = `r round(ECi_rating$estimate[[1]], 2)`, t = `r round(ECi_rating$statistic[[1]], 2)`, *p* = `r round(ECi_rating$p.value, 2)`|*r* = `r round(ECi_RAcc$estimate[[1]], 2)`, t = `r round(ECi_RAcc$statistic[[1]], 2)`, *p* = `r round(ECi_RAcc$p.value, 2)`|
|EC/D|*r* = `r round(ECd_rating$estimate[[1]], 2)`, t = `r round(ECd_rating$statistic[[1]], 2)`, *p* = `r round(ECd_rating$p.value, 2)`|*r* = `r round(ECd_RAcc$estimate[[1]], 2)`, t = `r round(ECd_RAcc$statistic[[1]], 2)`, *p* = `r round(ECd_RAcc$p.value, 2)`|
