---
title: "Trait curiosity and effects"
output: 
  html_document:
    fig_caption: yes
    highlight: default
    number_sections: no
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: true

  pdf_document:
    toc: yes
    toc_depth: 5
    number_sections: no
    highlight: tango
    latex_engine: xelatex
    fontsize: 12pt
---

\setmainfont{Noto Sans}
\setmathfont{Fira Code}
\colorlet{shadecolor}{gray!10}

<style>
body {
  font-size: 15px;
}

p.caption {
  font-weight: 500;
  font-style: italic;
}

code.r {
  font-family: Consolas, Monaco, monospace;
  font-size: 12px;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "html", cache=TRUE) # "latex" for PDF; "html" for html 
```

```{r load libraries, echo=FALSE}
library(data.table); 
```

```{r load the data, echo=FALSE}
load("../PilotData/IndividualData.RData")
load("../PilotData/ExcludedSubjectList.RData")
```

```{r remove excluded participants, echo=FALSE}
individual.average.data           <- individual.average.data[! SubjectNo %in% excluded.ps]
```

# Relationship between **Trait** and ratings
## *Curiosity* and ratings
```{r}
with(individual.average.data, cor.test(MeanCur, PC))
with(individual.average.data, cor.test(MeanCur, EC))
with(individual.average.data, cor.test(MeanCur, GN))
```

## *Interest* and ratings
```{r}
with(individual.average.data, cor.test(MeanInt, PC))
with(individual.average.data, cor.test(MeanInt, EC))
with(individual.average.data, cor.test(MeanInt, GN))
```

# Relationship between **Trait** and exploration duration
```{r}
with(individual.average.data, cor.test(MeanDur, PC))
with(individual.average.data, cor.test(MeanDur, EC))
with(individual.average.data, cor.test(MeanDur, GN))
```

# Relationship between **Trait** and overall memory performance
```{r}
with(individual.average.data, cor.test(MSAcc, PC))
with(individual.average.data, cor.test(MSAcc, EC))
with(individual.average.data, cor.test(MSAcc, GN))
```

# Relationship between **Trait** and overall memory enhancement
## Surprise
```{r}
with(individual.average.data, cor.test(SurME, PC))
with(individual.average.data, cor.test(SurME, EC))
with(individual.average.data, cor.test(SurME, GN))
```

## Pre-surprise
```{r}
with(individual.average.data, cor.test(PreSurME, PC))
with(individual.average.data, cor.test(PreSurME, EC))
with(individual.average.data, cor.test(PreSurME, GN))
```

