---
title: "Inside Item Recollection"
output:
  html_document:
    fig_caption: yes
    highlight: default
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: true
      smooth_scroll: true
  header-includes:
  - \usepackage{xcolor}
  - \usepackage{framed}
  - \usepackage{fontspec}
  html_notebook:
    
    fig_caption: yes
    highlight: default
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: true
  pdf_document:
    fig_caption: yes
    highlight: default
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 5
---

\setmainfont{Calibri}
\colorlet{shadecolor}{gray!10}
\color{red}

<style>
body {
  font-size: 15px;
}

p.caption {
  font-weight: 500;
  font-style: italic;
}

code.r {
  font-family: Consolas, Monaco, monospace;
  font-size: 12px;
}
</style>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "html", cache=TRUE) # "latex" for PDF
```

> This notebook focuses on item memory outside the rooms.

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(data.table); library(ggplot2); library(nlme); library(ez)
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
# load("~/Documents/OneDrive - Cardiff University/Projects/VRCuriosityMemory/PilotData/RawData/Pilot_02/.RData")
load("D:/OneDirve_CU/OneDrive - Cardiff University/Projects/VRCuriosityMemory/PilotData/RawData/Pilot_02/.RData")
# load("D:/Danlu.C - CU OneDrive/OneDrive - Cardiff University/VRCuriosityMemory/PilotData/RawData/Pilot_02/.RData")
```

# Overview of the data
The rooms were separated into *Familiar* and *Novel* groups. Participants explored the *Familiar* group at the beginning of the experiment. In the encoding task, they visisted both *Familiar* and *Novel* groups. Their item memory (i.e., in which room they saw the item) was tested in the memory test the next day of the encoding task. **Novelty benefits** on the item memory are examined by comparing the memory performance between the *Familiar* and *Novel* groups. 

Participants were also asked to rate how curious they felt about the room. The higher the rating is means they felt more curious about the room. Item memory as a function of curiosity rating was also examined for **curiosity benefits**.

Questionnaires on personal traits regarding curiosity were also administered to participants before the encoding task (i.e., PC and EC). Scores on these questionnaires might be able to predict the item memory or its relationship with curiosity rating. 

In the encoding task, there were 6 objects in each room. It is possbile that the item memory for the object to some extent depends on the order in which the object was seen. For example, it may be easier to remember where the first and last objects were seen as compared to those in the middle. 

# Visual inspection of the data
Removed participants who had lower hit rate than false alarm rate for recollection of outside items.

```{r Find out bad participants, echo=FALSE}
# bad.ps.less.strict <- NULL
# 
# for (this.p in participant.folders) {
#   this.data <- Encoding.Recall.Freq.Rsp[SubjectNo == this.p]
#   if (this.data[CorrObjResp == "New" & Response == "Seen"]$Frequency > this.data[CorrObjResp == "Seen" & Response == "Seen"]$Frequency) {
#     bad.ps.less.strict <- c(bad.ps.less.strict, this.p)
#   }
# }

Encoding.Recall.Freq.Grp$Type2 <- "Good"
Encoding.Recall.Freq.Grp[SubjectNo %in% bad.ps.less.strict]$Type2 <- "Bad"

Encoding.Recall.Freq.Rsp$Type2 <- "Good"
Encoding.Recall.Freq.Rsp[SubjectNo %in% bad.ps.less.strict]$Type2 <- "Bad"
```


```{r, echo=FALSE, fig.align='center', fig.width=7.2, fig.height=9, fig.cap='Figure 1. Response frequency for new and old items respectively for each individual participant.'}
ggplot(Encoding.Recall.Freq.Rsp, aes(x = Response, y = Frequency, group = CorrObjResp)) + theme_bw() +
  geom_rect(data = subset(Encoding.Recall.Freq.Rsp,Type2 == 'Bad'),aes(fill = Type2),xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,alpha = 0.1) +
  geom_point(size = 3, aes(color = CorrObjResp)) +
  geom_line(size = 0.75, aes(color = CorrObjResp)) +
  scale_x_discrete("Response", limits = c("Seen", "Familiar", "New")) +
  scale_color_brewer(palette = "Set1", labels = c("New items", "Old items")) +
  facet_wrap( ~ SubjectNo, ncol = 4) + 
  theme(strip.text = element_text(face = 'bold'),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 0.5) )
```


```{r, echo=FALSE, fig.align='center', fig.width=7.2, fig.height=9, fig.cap='Figure 2. Response frequency for new and old items respectively for each Familiar/Novel group and each individual participant.'}
ggplot(Encoding.Recall.Freq.Grp, aes(x = Response, y = Frequency, group = Group)) + theme_bw() +
  geom_rect(data = subset(Encoding.Recall.Freq.Grp,Type2 == 'Bad'),aes(fill = Type2),xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,alpha = 0.1) +
  geom_point(size = 3, aes(color = Group)) +
  geom_line(size = 0.75, aes(color = Group)) +
  scale_x_discrete("Response", limits = c("Seen", "Familiar", "New")) +
  scale_color_brewer(palette = "Set1", labels = c("Distractor", "In familiar room", "In novel room")) +
  facet_wrap( ~ SubjectNo, ncol = 4) + 
  theme(strip.text = element_text(face = 'bold'),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 0.5) )
```

# Novelty Benefits 
We hypothesised that the memory for the items outside the rooms should be better for the *novel* rooms than for the *familiar* rooms. 

## Compare mean accuracy between *novel* and *familiar* rooms
```{r meanbars, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3, fig.cap='Figure 3. Mean hit rate for recollect response respectively for Familiar and Novel rooms.'}
ggplot(InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict, .(MeanCorrSeenHit = mean(CorrSeenHit)), by = c("SubjectNo", "Group")], aes(x = Group, y = MeanCorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  labs(x = "Room novelty", y = "Mean Corrected Hit Rate")
```

```{r, echo = FALSE}
t.test(MeanCorrSeenHit ~ Group, data = InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict, .(MeanCorrSeenHit = mean(CorrSeenHit)), by = c("SubjectNo", "Group")], paired = TRUE)
```

## Item memory as a function of item order
### Visualise the data
#### Nonlinear
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6, fig.cap="Figure 4. Mean hit rate for seen response at each order (i.e., 1st, 2nd, 3rd, etc), respectively for familiar and novel rooms."}
ggplot(Encoding.Recall.Old.Novelty[!SubjectNo %in% bad.ps.less.strict], aes(x = ItemOrder, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "point", aes(group = Group, colour = Group), position = position_dodge(width = 0.2), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), se = FALSE, aes(group = Group, colour = Group)) +
  labs(x = "Item order", y = "Corrected Hit Rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

#### Linear
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6, fig.cap="Figure 4. Mean hit rate for seen response at each order (i.e., 1st, 2nd, 3rd, etc), respectively for familiar and novel rooms."}
ggplot(Encoding.Recall.Old.Novelty[!SubjectNo %in% bad.ps.less.strict], aes(x = ItemOrder, y = CorrSeenHit)) + theme_classic() +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, aes(group = Group, colour = Group), position = position_dodge(width = 0.4), size = 0.5, alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", aes(group = Group, colour = Group), position = position_dodge(width = 0.4), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, se = FALSE, aes(group = Group, colour = Group)) +
  labs(x = "Item order", y = "Corrected Hit Rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

### Testing novelty effect as a function of item order.
Build models with corrected hit rate as $y$ and then examine effects of novelty by comparing the models. 

* `baseline.item` is the model with only an intercept. 
* `order.model.linear.1` is the model with $\small ItemOrder$ included, showing the effects of item order. 
* `order.model.linear.2` is the model allowing the slope (i.e., relationship between item memory and item order) varying across participants. 
* `order.model.quad.1` and `order.model.quad.2` repectively included $\small ItemOrder^2$ and related random effects. 
* `novelty.model.1` is the model with $\small Group$ (i.e., *familiar* and *novel* rooms) included, examining the effects of novelty of the rooms on the intercept (i.e., mean item memory accuracy at the 1st order or overall if no difference in slope). 
* `novelty.model.2` is the model with interaction between $\small Group$ and $\small ItemOrder$ included, examining the effects of novelty on how item memory accuracy changes as a function of item order. 
* `novelty.model.3` included interaction between $\small Group$ and $\small ItemOrder^2$ for inestigating whether the pattern changes between *familiar* and *novel* groups. 

```{r, echo = FALSE}
Encoding.Recall.Old.Novelty$ItemOrderCt <- Encoding.Recall.Old.Novelty$ItemOrder - 1

Encoding.Recall.Old.Novelty$Group <- factor(Encoding.Recall.Old.Novelty$Group)
contrasts(Encoding.Recall.Old.Novelty$Group) <- c(1, 0)
```

```{r, echo = FALSE}
baseline.item <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo/Group, data = Encoding.Recall.Old.Novelty[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

order.model.linear.1 <- update(baseline.item, .~. + ItemOrderCt)
order.model.linear.2 <- update(order.model.linear.1, random = ~ 1 + ItemOrderCt|SubjectNo/Group)

order.model.quad.1   <- update(order.model.linear.1, .~. + I(ItemOrderCt^2))
# order.model.quad.2   <- update(order.model.quad.1, random = ~ 1 + ItemOrder + I(ItemOrder^2)|SubjectNo/Group)

novelty.model.1 <- update(order.model.quad.1, .~. + Group)
novelty.model.2 <- update(novelty.model.1, .~. + Group:ItemOrderCt)
novelty.model.3 <- update(novelty.model.2, .~. + Group:I(ItemOrderCt^2))

anova(baseline.item, order.model.linear.1, order.model.linear.2, order.model.quad.1, novelty.model.1, novelty.model.2, novelty.model.3)
```

Nothing significant.

#### Parameter estimation for the complete model
```{r, echo=FALSE}
summary(novelty.model.3)$tTable
```

### Collapse the order and novelty group
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6, fig.cap='Figure 7. Mean hit rate as a function of item order (Early vs. Late) and curiosity (Low vs. High).'}
ggplot(Encoding.Recall.Old.Order.Novelty[!SubjectNo %in% bad.ps.less.strict], aes(x = Group, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Room Novelty", y = "Corrected Hit Rate") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline      <- lme(CorrSeenHit ~ 1, random = ~1|SubjectNo/Group/ItemOrderType, data = Encoding.Recall.Old.Order.Novelty[!SubjectNo %in% bad.ps.less.strict], method = "ML")
NoveltyModel  <- update(baseline,     .~. + Group)
OrderModel    <- update(NoveltyModel,     .~. + ItemOrderType)
repeatedModel <- update(OrderModel, .~. + ItemOrderType : Group)

anova(baseline, NoveltyModel, OrderModel, repeatedModel)
```

No significant main effects or interaction.


# Curiosity Benefits
We hypothesed that the higher the curiosity rating was, the better the item memory should be.

## Mean accuracy of item memory as a function of curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3, fig.cap='Figure 5. Mean hit rate as a function of curiosity rating.'}
ggplot(InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict], aes(x = CuriosityRating, y = CorrSeenHit)) +
  stat_summary(fun.data = mean_cl_boot, na.rm = T, geom = "errorbar", width = 0.2) +
  stat_summary(fun.y = mean, na.rm = T, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(1:7)) +
  labs(x = "Curiosity rating", y = "Mean corrected hit rate") 
```

### Testing the relationship between mean accuracy of item memory and curiosity rating
Build models with item memory accuracy as $y$ and examine effects of curiosity rating by including it into the model and then comparing the model fits. 

* `baseline.rating` is the model with only an intercept, showing no change in item memory as a function of curiosity rating. 
* `rating.intercept` is the model with $\small CuriosityRating$ included, showing the effects of curiosity rating. 
* `rating.slope` is the model allowing the slope (i.e., relationship between item memory and curiosity rating) varying across participants. 

```{r, echo = FALSE}
baseline.rating <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo, data = InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + CuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating|SubjectNo)

anova(baseline.rating, rating.intercept, rating.slope)
```

Not significant.

### What about normalised curiosity rating?
```{r, echo = FALSE}
baseline.rating <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo, data = InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + NCuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + NCuriosityRating|SubjectNo)

anova(baseline.rating, rating.intercept, rating.slope)
```
Still not significant.

## Does the relationship with curiosity rating depend on item order?
### Curiosity Rating
```{r, echo=FALSE, fig.align='center', fig.width=10.8, fig.height=3, fig.cap='Figure 6. Mean hit rate across participants as a function of curiosity rating for each order at which the item was seen (I.e., 1st, 2nd, 3rd, etc.).'}
ggplot(Encoding.Recall.Old.CuriosityRating[!SubjectNo %in% bad.ps.less.strict], aes(x = CuriosityRating, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  labs(x = "Curiosity rating", y = "Corrected Hit Rate") +
  scale_x_continuous(breaks = c(1:7)) +
  facet_wrap( ~ ItemOrder, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```


### Testing the effect of item order
Build models with corrected hit rate as $y$ and examine effects of curiosity rating and item order by comparing the models. 

* `item.model.linear.1` is the model with $\small ItemOrder$ included (in addition to $\small CuriosityRating$), showing the effects of item order. 
* `item.model.linear.2` is the model allowing the slope (i.e., relationship between item memory and item order) varying across participants. 
* `item.model.linear.3` is the model with the interaction between $\small ItemOrders$ and $\small CuriosityRating$ included.
* `item.model.quad.1` and `item.model.quad.2` repectively included $\small ItemOrder^2$ and related random effects. 
* `item.model.quad.3` included interaction between $\small ItemOrder^2$ and $\small CuriosityRating$ for inestigating whether the pattern changes as a function of *curiosity rating*. 

```{r, echo = FALSE}
Encoding.Recall.Old.CuriosityRating$ItemOrderCt <- Encoding.Recall.Old.CuriosityRating$ItemOrder - 1
```

```{r}
baseline.item <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo, data = Encoding.Recall.Old.CuriosityRating[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.item, .~. + CuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating | SubjectNo)

item.model.linear.1     <- update(rating.slope, .~. + ItemOrderCt)
item.model.linear.2     <- update(item.model.linear.1, random = ~1+CuriosityRating + ItemOrderCt|SubjectNo)
item.model.linear.3     <- update(item.model.linear.2, .~. + ItemOrderCt : CuriosityRating)

item.model.quad.1       <- update(item.model.linear.3, .~. + I(ItemOrder^2))
# item.model.quad.2       <- update(item.model.quad.1,   random = ~1+CuriosityRating+ItemOrder+I(ItemOrder^2)|SubjectNo) # excluding this model because singularity issue (perhaps the model was getting too complex to be calculated)
item.model.quad.3       <- update(item.model.quad.1,   .~. + I(ItemOrder^2) : CuriosityRating)

anova(baseline.item, rating.intercept, rating.slope, item.model.linear.1, item.model.linear.2, item.model.linear.3, item.model.quad.1, item.model.quad.3)
```

There was a significant interaction between curiosity rating and item order (quadratic trend), *p* = 0.038.

```{r}
summary(item.model.quad.3)
```
For the first item, there was a significant positive correlation between recollection and curiosity rating, *p* = 0.014. The correlation become weaker for the items that were seen later, both in terms of linear trend (*p* = 0.019) and quadratic trend (*p* = 0.038).


#### What about normalised curiosity rating?
```{r, echo = FALSE}
Encoding.Recall.Old.CuriosityRatingN$ItemOrderCt <- Encoding.Recall.Old.CuriosityRating$ItemOrder - 1
```

```{r}
baseline.item <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo, data = Encoding.Recall.Old.CuriosityRatingN[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.item, .~. + NCuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + NCuriosityRating | SubjectNo)

item.model.linear.1     <- update(rating.slope, .~. + ItemOrderCt)
item.model.linear.2     <- update(item.model.linear.1, random = ~1+NCuriosityRating + ItemOrderCt|SubjectNo)
item.model.linear.3     <- update(item.model.linear.2, .~. + ItemOrderCt : NCuriosityRating)

item.model.quad.1       <- update(item.model.linear.3, .~. + I(ItemOrderCt^2))
# item.model.quad.2       <- update(item.model.quad.1,   random = ~1+CuriosityRating+ItemOrder+I(ItemOrder^2)|SubjectNo) # excluding this model because singularity issue (perhaps the model was getting too complex to be calculated)
item.model.quad.3       <- update(item.model.quad.1,   .~. + I(ItemOrderCt^2) : NCuriosityRating)

anova(baseline.item, rating.intercept, rating.slope, item.model.linear.1, item.model.linear.2, item.model.linear.3, item.model.quad.1, item.model.quad.3)
```
Similar to the results on the original curiosity ratings.

#### Parameter estimation for the optimal model
```{r}
summary(item.model.quad.3 )$tTable
```

### Collapse the order and curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6, fig.cap='Figure 7. Mean hit rate as a function of item order (Early vs. Late) and curiosity (Low vs. High).'}
ggplot(Encoding.Recall.Old.Order.CuriosityType[!SubjectNo %in% bad.ps.less.strict], aes(x = CuriosityRatingType, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Hit rate for recollection") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline <- lme(CorrSeenHit ~ 1, random = ~ 1| SubjectNo/CuriosityRatingType/ItemOrderType, data = Encoding.Recall.Old.Order.CuriosityType[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel   <- update(baseline,       .~. + CuriosityRatingType)
orderModel       <- update(curiosityModel, .~. + ItemOrderType)
interactionModel <- update(orderModel,     .~. + CuriosityRatingType : ItemOrderType)

anova(baseline, curiosityModel, orderModel, interactionModel)
```

No significant.

#### Linear trend respectivley for High and Low curiosity groups
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6}
ggplot(Encoding.Recall.Old.CuriosityType[!SubjectNo %in% bad.ps.less.strict], aes(x = ItemOrder, y = CorrSeenHit)) + theme_classic() +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, aes(group = CuriosityRatingType, colour = CuriosityRatingType), position = position_dodge(width = 0.4), size = 0.5, alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", aes(group = CuriosityRatingType, colour = CuriosityRatingType), position = position_dodge(width = 0.4), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, se = FALSE, aes(group = CuriosityRatingType, colour = CuriosityRatingType)) +
  labs(x = "Item order", y = "Corrected Hit Rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Low Curiosity", "High Curiosity")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

```{r}
Encoding.Recall.Old.CuriosityType$ItemOrderCt <- Encoding.Recall.Old.CuriosityType$ItemOrder - 1

baseline <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo/CuriosityRatingType, data = Encoding.Recall.Old.CuriosityType[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

orderModel.linear.1   <- update(baseline,              .~. + ItemOrderCt)
orderModel.linear.2   <- update(orderModel.linear.1,   random = ~ 1 + ItemOrderCt|SubjectNo/CuriosityRatingType)

curiosityModel        <- update(orderModel.linear.2,   .~. + CuriosityRatingType)
curiosityModel.linear <- update(curiosityModel,        .~. + CuriosityRatingType : ItemOrderCt)

anova(baseline, orderModel.linear.1, orderModel.linear.2, curiosityModel, curiosityModel.linear)
```
There was a marginally signficant interaction, *p* = 0.054.

```{r}
summary(curiosityModel.linear)$tTable
```
For low curiosity, there was a significant positive correlation with item order, *p* = 0.037, which was marginally steeper than high curiosity group, *p* = 0.055.

### Try another way to calculate "High" and "Low" curiosity groups
> "High" - higher than mean; "Low" - lower than mean

#### Compare "High" and "Low" groups
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3, fig.cap='Figure 3. Mean hit rate for recollect response respectively for Familiar and Novel rooms.'}
ggplot(Encoding.Recall.Old.Collapsed.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], aes(x = RatingGroup, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  labs(x = "Curiosity level", y = "Mean Corrected Hit Rate")
```

```{r, echo = FALSE}
t.test(CorrSeenHit ~ RatingGroup, data = Encoding.Recall.Old.Collapsed.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], paired = T)
```

```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6}
ggplot(Encoding.Recall.Old.Order.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], aes(x = RatingGroup, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Corrected hit rate for recollection") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline <- lme(CorrSeenHit ~ 1, random = ~ 1| SubjectNo/RatingGroup/ItemOrderType, data = Encoding.Recall.Old.Order.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel   <- update(baseline,       .~. + RatingGroup)
orderModel       <- update(curiosityModel, .~. + ItemOrderType)
interactionModel <- update(orderModel,     .~. + RatingGroup : ItemOrderType)

anova(baseline, curiosityModel, orderModel, interactionModel)
```

No significant main effects.

#### Linear trend respectivley for High and Low curiosity groups
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6}
ggplot(Encoding.Recall.Old.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], aes(x = ItemOrder, y = CorrSeenHit)) + theme_classic() +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, aes(group = RatingGroup, colour = RatingGroup), position = position_dodge(width = 0.4), size = 0.5, alpha = 0.5) +
  stat_summary(fun.y = mean, geom = "point", aes(group = RatingGroup, colour = RatingGroup), position = position_dodge(width = 0.4), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, se = FALSE, aes(group = RatingGroup, colour = RatingGroup)) +
  labs(x = "Item order", y = "Corrected Hit Rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Low Curiosity", "High Curiosity")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

```{r}
Encoding.Recall.Old.CuriosityType.MeanSep$ItemOrderCt <- Encoding.Recall.Old.CuriosityType.MeanSep$ItemOrder - 1

baseline <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo/RatingGroup, data = Encoding.Recall.Old.CuriosityType.MeanSep[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

orderModel.linear.1   <- update(baseline,              .~. + ItemOrderCt)
orderModel.linear.2   <- update(orderModel.linear.1,   random = ~ 1 + ItemOrderCt|SubjectNo/RatingGroup)

curiosityModel        <- update(orderModel.linear.2,   .~. + RatingGroup)
curiosityModel.linear <- update(curiosityModel,        .~. + RatingGroup : ItemOrderCt)

anova(baseline, orderModel.linear.1, orderModel.linear.2, curiosityModel, curiosityModel.linear)
```
No significant main effect.

# Curiosity and novelty
## Testing the effects of curiosity rating and novelty together
Build models with item memory accuracy as $y$ and examine effects of curiosity rating and novelty together by including them into the model separately and then comparing the model fits. 

* `baseline.rating` is the model with only an intercept, showing no change in item memory as a function of curiosity rating. 
* `rating.intercept` is the model with $\small CuriosityRating$ included, showing the effects of curiosity rating. 
* `rating.slope` is the model allowing the slope (i.e., relationship between item memory and curiosity rating) varying across participants. 
* `novelty.model` is the model with $\small Group$ (i.e., *familiar* and *novel* rooms) included, examining the effects of novelty of the rooms on the intercept (i.e., mean item memory accuracy at the 1st order or overall if no difference in slope). 
* `interaction.model` is the model with interaction between $\small Group$ and $\small CuriosityRating$ included, examining the effects of novelty on how item memory accuracy changes as a function of item order. 

``` {r, echo = FALSE}
baseline.rating <- lme(CorrSeenHit ~ 1, random = ~ 1|SubjectNo/Group, data = InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + CuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating|SubjectNo/Group)

novelty.model.1 <- update(rating.slope, .~. + Group)

interaction.model <- update(novelty.model.1, .~. + Group:CuriosityRating)

anova(baseline.rating, rating.intercept, rating.slope, novelty.model.1, interaction.model)
```

### Check the complete model
```{r, echo=FALSE}
summary(interaction.model)$tTable
```


## What about the other way around
```{r, echo=FALSE}
novelty.model.1 <- update(baseline.rating, .~. + Group)

rating.model.1 <- update(novelty.model.1, .~. + CuriosityRating)
rating.model.2 <- update(rating.model.1, random = ~ 1 + CuriosityRating|SubjectNo/Group)

interaction.model <- update(rating.model.2, .~. + Group:CuriosityRating)

anova(baseline.rating, novelty.model.1, rating.model.1, rating.model.2, interaction.model)
```

### Check the complete model
```{r, echo=FALSE}
summary(interaction.model)$tTable
```

## Check the collapsed data
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6}
ggplot(Encoding.Recall.Old.Interaction[!SubjectNo %in% bad.ps.less.strict], aes(x = CuriosityRatingType, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Hit rate for recollection") +
  facet_wrap( ~ Group, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

### Alternative way to collapse data
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6}
ggplot(Encoding.Recall.Old.Interaction.MeanSep[!SubjectNo %in% bad.ps.less.strict], aes(x = RatingGroup, y = CorrSeenHit)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Corrected hit rate for recollection") +
  facet_wrap( ~ Group, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

```{r, echo = FALSE}
baseline <- lme(CorrSeenHit ~ 1, random = ~ 1| SubjectNo/RatingGroup/Group, data = Encoding.Recall.Old.Interaction.MeanSep[!SubjectNo %in% bad.ps.less.strict], method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel    <- update(baseline,        .~. + RatingGroup)
noveltyModel      <- update(curiosityModel,  .~. + Group)
interactionModel  <- update(noveltyModel,    .~. + RatingGroup : Group)

anova(baseline, curiosityModel, noveltyModel, interactionModel)
```

No significant main effect.

# Curiosity effects in the *Novel* group
## Mean accuracy of item memory as a function of curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3}
ggplot(InsideObjectsMemory[!SubjectNo %in% bad.ps.less.strict & Group == "Novel"], aes(x = CuriosityRating, y = CorrSeenHit)) +
  stat_summary(fun.data = mean_cl_boot, na.rm = T, geom = "errorbar", width = 0.2) +
  stat_summary(fun.y = mean, na.rm = T, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(1:7)) +
  labs(x = "Curiosity rating", y = "Mean hit rate for recollection") 
```