---
title: "Outside Context Memory"
output:
  html_document:
    fig_caption: yes
    highlight: default
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: true
      smooth_scroll: true
  header-includes:
  - \usepackage{xcolor}
  - \usepackage{framed}
  - \usepackage{fontspec}
  html_notebook:
    
    fig_caption: yes
    highlight: default
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: true
  pdf_document:
    fig_caption: yes
    highlight: default
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 5
---

\setmainfont{Calibri}
\colorlet{shadecolor}{gray!10}
\color{red}

<style>
body {
  font-size: 15px;
}

p.caption {
  font-weight: 500;
  font-style: italic;
}

code.r {
  font-family: Consolas, Monaco, monospace;
  font-size: 12px;
}
</style>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
options(knitr.table.format = "html", cache=TRUE) # "latex" for PDF
```

> This notebook focuses on context memory outside the rooms. 

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(data.table); library(ggplot2); library(nlme); library(Hmisc); library(multcomp)
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
# load("~/Documents/OneDrive - Cardiff University/Projects/VRCuriosityMemory/PilotData/RawData/Pilot_01/.RData")
load("D:/OneDirve_CU/OneDrive - Cardiff University/Projects/VRCuriosityMemory/PilotData/RawData/Pilot_01/.RData")
# load("D:/Danlu.C - CU OneDrive/OneDrive - Cardiff University/VRCuriosityMemory/PilotData/RawData/Pilot_01/.RData")
```

# Overview of the data
The rooms were separated into *Familiar* and *Novel* groups. Participants explored the *Familiar* group at the beginning of the experiment. In the encoding task, they visisted both *Familiar* and *Novel* groups. Their context memory (i.e., in which room they saw the item) was tested in the memory test the next day of the encoding task. **Novelty benefits** on the context memory are examined by comparing the memory performance between the *Familiar* and *Novel* groups. 

Participants were also asked to rate how curious they felt about the room. The higher the rating is means they felt more curious about the room. Context memory as a function of curiosity rating was also examined for **curiosity benefits**.

Questionnaires on personal traits regarding curiosity were also administered to participants before the encoding task (i.e., PC and EC). Scores on these questionnaires might be able to predict the context memory or its relationship with curiosity rating. 

In the encoding task, there were 6 objects outside each room. It is possbile that the context memory for the object to some extent depends on the order in which the object was seen. For example, it may be easier to remember where the first and last objects were seen as compared to those in the middle. Particularly, if the participant became more curious when getting closer to the room, then one would expect that the performance increases as a function of item order. 

```{r Find out bad participants, echo=FALSE}
# bad.ps.less.strict <- NULL
# 
# for (this.p in participant.folders) {
#   this.data <- Curiosity.Recall.Freq.Rsp[SubjectNo == this.p]
#   if (this.data[CorrObjResp == "New" & Response == "Seen"]$Frequency > this.data[CorrObjResp == "Seen" & Response == "Seen"]$Frequency) {
#     bad.ps.less.strict <- c(bad.ps.less.strict, this.p)
#   }
# }

# OutsideObjectsMemory$Type2 <- "Good"
# OutsideObjectsMemory[SubjectNo %in% bad.ps.less.strict]$Type2 <- "Bad"

# Curiosity.Recall.Old.Corr.Freq$Type2 <- "Good"
# Curiosity.Recall.Old.Corr.Freq[SubjectNo %in% bad.ps.less.strict]$Type2 <- "Bad"
```

# Individual performance
## An overview of individual context memory performance as a function of room.
```{r, echo=FALSE, fig.align='center', fig.width=7.2, fig.height=8.1, fig.cap='Figure 1. Mean accuracy for context memory respectively for each room and each individual participant.'}
ggplot(OutsideObjectsMemory, aes(x = Room, y = ContextAccuracy)) +
  # geom_rect(data = subset(OutsideObjectsMemory,Type2 == 'Bad'),aes(fill = Type2),xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,alpha = 0.1) +
  geom_line( aes(group = Group, colour = Group)) +
  geom_point( aes (colour = Group), size = 3) +
  facet_wrap( ~ SubjectNo, ncol = 4) +
  labs(x = "Room ", y = "Accuracy for context memory") +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1))
```

<!-- ## For correctly labelled distractor items -->
```{r, eval = FALSE, echo=FALSE, fig.align='center', fig.width=6.4, fig.height=4.2, fig.cap='Figure 2. Frequency of correctly labelled distractor objects for each individual participant.'}
ggplot(Curiosity.Recall.New.Freq, aes(x = Response, y = Frequency)) +
  geom_point( size = 1.5) +
  facet_wrap( ~ SubjectNo, ncol = 4) +
  labs(x = "Response ", y = "Frequency (%)") 
```

<!-- ## For correctly recalled items -->
```{r, eval = FALSE, echo=FALSE, fig.align='center', fig.width=7.2, fig.height=8.1, fig.cap='Figure 3. Frequency of correctly labelled distractor objects for each individual participant.'}
ggplot(Curiosity.Recall.Old.Corr.Freq, aes(x = Response, y = Frequency)) +
  # geom_rect(data = subset(Curiosity.Recall.Old.Corr.Freq,Type2 == 'Bad'),aes(fill = Type2),xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,alpha = 0.1) +
  geom_line( aes(group = Group, colour = Group)) +
  geom_point( size = 3, aes(group = Group, colour = Group)) +
  facet_wrap( ~ SubjectNo, ncol = 4) +
  labs(x = "Response ", y = "Frequency (%)") +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(axis.text.x = element_text(angle = 45, size = 10, hjust = 1))
```

# Novelty Benefits 
We predicted that the context memory should be better for the *novel* rooms than for the *familiar* rooms.

## Compare mean accuracy between *novel* and *familiar* rooms
```{r meanbars, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3, fig.cap='Figure 2. Mean accuracy for context memory respectively for Familiar and Novel rooms.'}
ggplot(OutsideObjectsMemory[, .(MeanCorrContextAccuracy = mean(CorrContextAccuracy)), by = c("SubjectNo", "Group")], aes(x = Group, y = MeanCorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  labs(x = "Room novelty", y = "Mean accuracy for context memory")
```

```{r, echo = FALSE}
t.test(MeanCorrContextAccuracy ~ Group, data = OutsideObjectsMemory[, .(MeanCorrContextAccuracy = mean(CorrContextAccuracy)), by = c("SubjectNo", "Group")], paired = TRUE)
```
Unfortunately not significant.

## Context memory as a function of item order
### Visualise the data
#### Nonlinear
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6, fig.cap="Figure 3. Mean accuracy of context memory for items at each order (i.e., 1st, 2nd, 3rd, etc), respectively for familiar and novel rooms."}
ggplot(Curiosity.Recall.Old.Novelty, aes(x = ItemOrder, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "point", aes(group = Group, colour = Group), position = position_dodge(width = 0.2), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), se = FALSE, aes(group = Group, colour = Group)) +
  labs(x = "Item order", y = "Corrected hit rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

#### Linear
```{r, echo = FALSE, fig.align= 'center', fig.width=4.8, fig.height=3.6}
ggplot(Curiosity.Recall.Old.Novelty, aes(x = ItemOrder, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "point", aes(group = Group, colour = Group), position = position_dodge(width = 0.2), size = 2) +
  stat_smooth(method = "lm", formula = y ~ x, se = FALSE, aes(group = Group, colour = Group)) +
  labs(x = "Item order", y = "Corrected hit rate") +
  scale_x_continuous(breaks = c(1:6)) +
  scale_color_brewer(palette = "Set1", labels = c("Familiar rooms", "Novel rooms")) +
  theme(legend.title = element_blank(),
        axis.title = element_text(face = "bold"))
```

### Testing novelty effect as a function of item order by fitting mixed models
Build models with context memory accuracy as $y$ and then examine effects of item order and novelty by comparing the models. 

* `baseline.context` is the model with only an intercept. 
* `order.model.linear.1` is the model with $\small ItemOrder$ included, showing the effects of item order. 
* `order.model.linear.2` is the model allowing the slope (i.e., relationship between context memory and item order) varying across participants. 
* `order.model.quad.1` and `order.model.quad.2` repectively included $\small ItemOrder^2$ and related random effects. 
* `novelty.model.1` is the model with $\small Group$ (i.e., *familiar* and *novel* rooms) included, examining the effects of novelty of the rooms on the intercept (i.e., mean context memory accuracy at the 1st order or overall if no difference in slope). 
* `novelty.model.2` is the model with interaction between $\small Group$ and $\small ItemOrder$ included, examining the effects of novelty on how context memory accuracy changes as a function of item order. 
* `novelty.model.3` included interaction between $\small Group$ and $\small ItemOrder^2$ for inestigating whether the pattern changes between *familiar* and *novel* groups. 

```{r, echo = FALSE}
baseline.context <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo/Group, data = Curiosity.Recall.Old.Novelty, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

order.model.linear.1 <- update(baseline.context, .~. + ItemOrder)
# order.model.linear.2 <- update(order.model.linear.1, random = ~ 1 + ItemOrder|SubjectNo/Group)

# order.model.quad.1   <- update(order.model.linear.1, .~. + I(ItemOrder^2))
# order.model.quad.2   <- update(order.model.quad.1, random = ~ 1 + ItemOrder + I(ItemOrder^2)|SubjectNo)

novelty.model.1 <- update(order.model.linear.1, .~. + Group)
novelty.model.2 <- update(novelty.model.1, .~. + Group:ItemOrder)
# novelty.model.3 <- update(novelty.model.2, .~. + Group:I(ItemOrder^2))

anova(baseline.context, order.model.linear.1, novelty.model.1, novelty.model.2)
```

Including interaction between $\small Group$ and $\small ItemOrder$ significantly improved the model fit, suggesting the pattern of context memory accuracy as a function of item order is different between *familiar* and *novel* rooms.


### Collapse the order
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6, fig.cap='Figure 4. Mean hit rate as a function of item order (Early vs. Late) and curiosity (Low vs. High).'}
ggplot(Curiosity.Recall.Old.Order.Novelty, aes(x = Group, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Hit rate for recollection") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline         <- lme(CorrContextAccuracy ~ 1, random = ~ 1| SubjectNo/Group/ItemOrderType, data = Curiosity.Recall.Old.Order.Novelty, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

noveltyModel     <- update(baseline,     .~. + Group)
orderModel       <- update(noveltyModel, .~. + ItemOrderType)
interactionModel <- update(orderModel,   .~. + Group : ItemOrderType)

anova(baseline, noveltyModel, orderModel, interactionModel)

summary(interactionModel)$tTable
```

No interaction. Novel > Familiar for the *early* group but failed to reach significance.


# Curiosity Benefits
Here I checked how accurach of context memory changes as a function of curiosity rating. We hypothesised that the more curiosity the participant felt about the room (higher ratings) the better the context memory. 

## Mean accuracy of context memory as a function of curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3, fig.cap='Figure 5. Mean accuracy for context memory as a function of curiosity rating.'}
ggplot(OutsideObjectsMemory, aes(x = CuriosityRating, y = CorrContextAccuracy)) +
  stat_summary(fun.data = mean_cl_boot, na.rm = T, geom = "errorbar", width = 0.2) +
  stat_summary(fun.y = mean, na.rm = T, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(1:7)) +
  labs(x = "Curiosity rating", y = "Corrected hit rate") 
```
Against our prediction, there seems to be a negative correlation between curiosity rating and context memory.

### Testing the relationship between mean accuracy of context memory and curiosity rating
Build models with context memory accuracy as $y$ and cexamine effects of curiosity rating by including it into the model and then comparing the model fits. 

* `baseline.rating` is the model with only an intercept, showing no change in context memory as a function of curiosity rating. 
* `rating.intercept` is the model with $\small CuriosityRating$ included, showing the effects of curiosity rating. 
* `rating.slope` is the model allowing the slope (i.e., relationship between context memory and curiosity rating) varying across participants. 

```{r, echo = FALSE}
baseline.rating <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo, data = OutsideObjectsMemory, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + CuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating|SubjectNo)

anova(baseline.rating, rating.intercept, rating.slope)
```

#### Parameter estimates in the complete model
```{r}
summary(rating.intercept)$tTable
```

### `r text_spec("Using normalised curiosity ratings", background = "#D05A6E", color = "white", bold = T, font_size = 15)`.
```{r, echo = FALSE}
baseline.rating <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo, data = OutsideObjectsMemory, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + NCuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + NCuriosityRating|SubjectNo)

anova(baseline.rating, rating.intercept, rating.slope)
```

```{r}
summary(rating.intercept)$tTable
```

## Does the relationship with curiosity rating depend on item order?
```{r, echo=FALSE, fig.align='center', fig.width=10.8, fig.height=3, fig.cap='Figure 6. Mean accuracy across participants for context memory as a function of curiosity rating for each order at which the item was seen (I.e., 1st, 2nd, 3rd, etc.).'}
ggplot(Curiosity.Recall.Old, aes(x = CuriosityRating, y = CorrContextAccuracy)) + 
  stat_summary(fun.y = mean, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  labs(x = "Curiosity rating", y = "Accuracy of Context Memory") +
  scale_x_continuous(breaks = c(1:7)) +
  facet_wrap( ~ ItemOrder, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```
For all the orders (except the 2nd), the relationship between curiosity rating and context memory looks negative.

### Testing the effect of item order
Build models with context memory accuracy as $y$ and examine effects of curioity rating and item order by comparing the models. 

* `item.model.linear.1` is the model with $\small ItemOrder$ included (in addition to $\small CuriosityRating$), showing the effects of item order. 
* `item.model.linear.2` is the model allowing the slope (i.e., relationship between context memory and item order) varying across participants. 
* `item.model.linear.3` is the model with the interaction between $\small ItemOrders$ and $\small CuriosityRating$ included.
* `item.model.quad.1` and `item.model.quad.2` repectively included $\small ItemOrder^2$ and related random effects. 
* `item.model.quad.3` included interaction between $\small ItemOrder^2$ and $\small CuriosityRating$ for inestigating whether the pattern changes as a function of *curiosity rating*.

```{r}
baseline.context <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo, data = Curiosity.Recall.Old, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.context, .~. + CuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating | SubjectNo)

item.model.linear.1     <- update(rating.slope, .~. + ItemOrder)
# item.model.linear.2     <- update(item.model.linear.1, random = list(~1+CuriosityRating|SubjectNo, ~1+ItemOrder|SubjectNo))
item.model.linear.3     <- update(item.model.linear.1, .~. + ItemOrder : CuriosityRating)

# item.model.quad.1       <- update(item.model.linear.3, .~. + I(ItemOrder^2))
# item.model.quad.2       <- update(item.model.quad.1,   random = list(~1+CuriosityRating|SubjectNo, ~1+ItemOrder+I(ItemOrder^2)|SubjectNo)) # excluding this model because singularity issue (perhaps the model was getting too complex to be calculated)
# item.model.quad.3       <- update(item.model.quad.1,   .~. + I(ItemOrder^2) : CuriosityRating)

anova(baseline.context, rating.intercept, rating.slope, item.model.linear.1, item.model.linear.3)
```

No significant effect, although curiosity rating is close to significance, *p* = 0.052.

#### What about **normalised ratings**?
```{r}
baseline.context <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo, data = Curiosity.Recall.Old, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.context, .~. + NCuriosityRating)
rating.slope     <- update(rating.intercept, random = ~ 1 + NCuriosityRating | SubjectNo)

item.model.linear.1     <- update(rating.slope, .~. + ItemOrder)
# item.model.linear.2     <- update(item.model.linear.1, random = list(~1+CuriosityRating|SubjectNo, ~1+ItemOrder|SubjectNo))
item.model.linear.3     <- update(item.model.linear.1, .~. + ItemOrder : NCuriosityRating)

# item.model.quad.1       <- update(item.model.linear.3, .~. + I(ItemOrder^2))
# item.model.quad.2       <- update(item.model.quad.1,   random = list(~1+CuriosityRating|SubjectNo, ~1+ItemOrder+I(ItemOrder^2)|SubjectNo)) # excluding this model because singularity issue (perhaps the model was getting too complex to be calculated)
# item.model.quad.3       <- update(item.model.quad.1,   .~. + I(ItemOrder^2) : CuriosityRating)

anova(baseline.context, rating.intercept, rating.slope, item.model.linear.1, item.model.linear.3)
```
The same.

### Collapse the order and curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6, fig.cap='Figure 7. Mean hit rate as a function of item order (Early vs. Late) and curiosity (Low vs. High).'}
ggplot(Curiosity.Recall.Old.Order.CuriosityType, aes(x = CuriosityRatingType, y = CorrContextAccuracy)) + 
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Corrected Context Accuracy") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline      <- lme(CorrContextAccuracy ~ 1, random = ~1| SubjectNo/CuriosityRatingType/ItemOrderType, data = Curiosity.Recall.Old.Order.CuriosityType , method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel   <- update(baseline,         .~. + CuriosityRatingType)
orderModel       <- update(curiosityModel,   .~. + ItemOrderType)
interactionModel <- update(orderModel,       .~. + CuriosityRatingType : ItemOrderType)

anova(baseline, curiosityModel, orderModel, interactionModel)

summary(curiosityModel)$tTable
```
A main effect of curiosity rating, but no interaction.

### Try another way to calculate "High" and "Low" curiosity groups
> "High" - higher than mean; "Low" - lower than mean

#### Compare "High" and "Low" groups
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3}
ggplot(Curiosity.Recall.Old.Collapsed.CuriosityType.MeanSep, aes(x = RatingGroup, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  labs(x = "Curiosity level", y = "Corrected hit rate")
```

```{r, echo = FALSE}
t.test(CorrContextAccuracy ~ RatingGroup, data = Curiosity.Recall.Old.Collapsed.CuriosityType.MeanSep, paired = T)
```

Significant.

```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6}
ggplot(Curiosity.Recall.Old.Order.CuriosityType.MeanSep, aes(x = RatingGroup, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity level", y = "Mean corrected hit rate") +
  facet_wrap( ~ ItemOrderType, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline      <- lme(CorrContextAccuracy ~ 1, random = ~1| SubjectNo/RatingGroup/ItemOrderType, data = Curiosity.Recall.Old.Order.CuriosityType.MeanSep , method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel   <- update(baseline,         .~. + RatingGroup)
orderModel       <- update(curiosityModel,   .~. + ItemOrderType)
interactionModel <- update(orderModel,       .~. + RatingGroup : ItemOrderType)

anova(baseline, curiosityModel, orderModel, interactionModel)
```

A main effect of curiosity and a significant interaction.

```{r, echo = FALSE}
contrast.matrix <- rbind(
  "Early: High - Low"     = c(0, 1, 0, 0),
  "Late:  High - Low"     = c(0, 1, 0, 1))
postHoc <- glht(interactionModel, contrast.matrix)
summary(postHoc, test = adjusted("none"))
```

High > Low significantly for *early* group.

# Curiosity and novelty
## Testing the effects of curiosity rating and novelty together
Build models with context memory accuracy as $y$ and examine effects of curiosity rating and novelty together by including them into the model separately and then comparing the model fits. 

* `baseline.rating` is the model with only an intercept, showing no change in context memory as a function of curiosity rating. 
* `rating.intercept` is the model with $\small CuriosityRating$ included, showing the effects of curiosity rating. 
* `rating.slope` is the model allowing the slope (i.e., relationship between context memory and curiosity rating) varying across participants. 
* `novelty.model` is the model with $\small Group$ (i.e., *familiar* and *novel* rooms) included, examining the effects of novelty of the rooms on the intercept (i.e., mean context memory accuracy at the 1st order or overall if no difference in slope). 
* `interaction.model` is the model with interaction between $\small Group$ and $\small CuriosityRating$ included, examining the effects of novelty on how context memory accuracy changes as a function of item order. 

``` {r, echo = FALSE}
baseline.rating <- lme(CorrContextAccuracy ~ 1, random = ~ 1|SubjectNo/Group, data = OutsideObjectsMemory, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE), na.action = na.exclude)

rating.intercept <- update(baseline.rating, .~. + CuriosityRating)
# rating.slope     <- update(rating.intercept, random = ~ 1 + CuriosityRating|SubjectNo/Group)

novelty.model.1 <- update(rating.intercept, .~. + Group)

interaction.model <- update(novelty.model.1, .~. + Group:CuriosityRating)

anova(baseline.rating, rating.intercept, novelty.model.1, interaction.model)
```

## What about the other way around
```{r, echo=FALSE}
novelty.model.1 <- update(baseline.context, .~. + Group)

rating.model.1 <- update(novelty.model.1, .~. + CuriosityRating)
rating.model.2 <- update(rating.model.1, random = ~ 1 + CuriosityRating|SubjectNo/Group)

interaction.model <- update(rating.model.2, .~. + Group:CuriosityRating)

anova(baseline.context, novelty.model.1, rating.model.1, rating.model.2, interaction.model)
```

## Check the collapsed data
```{r, echo=FALSE, fig.align='center', fig.width=4.2, fig.height=3.6}
ggplot(Curiosity.Recall.Old.Interaction.MeanSep, aes(x = RatingGroup, y = CorrContextAccuracy)) +
  stat_summary(fun.y = mean, geom = "bar", size = 2, fill = "grey50") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2, position = position_dodge(width = 0.9)) +
  labs(x = "Curiosity rating", y = "Mean corrected hit rate") +
  facet_wrap( ~ Group, nrow = 1) +
  theme(strip.text = element_text(face = "bold", size = 11),
        axis.title = element_text(face = "bold"))
```

#### Stats on it
```{r, echo = FALSE}
baseline <- lme(CorrContextAccuracy ~ 1, random = ~ 1| SubjectNo/RatingGroup/Group, data = Curiosity.Recall.Old.Interaction.MeanSep, method = "ML", control = list(msMaxIter = 500, opt = "optim", msVerbose=FALSE))

curiosityModel   <- update(baseline, .~. + RatingGroup)
noveltyModel     <- update(curiosityModel, .~. + Group)
interactionModel <- update(noveltyModel,  .~. + RatingGroup : Group)

anova(baseline, curiosityModel, noveltyModel, interactionModel)

summary(interactionModel)$tTable
```


# Curiosity effects in the *Novel* group
## Mean accuracy of item memory as a function of curiosity rating
```{r, echo=FALSE, fig.align='center', fig.width=3.6, fig.height=3}
ggplot(OutsideObjectsMemory[ Group == "Novel"], aes(x = CuriosityRating, y = CorrContextAccuracy)) +
  stat_summary(fun.data = mean_cl_boot, na.rm = T, geom = "errorbar", width = 0.2) +
  stat_summary(fun.y = mean, na.rm = T, geom = "point", size = 2) +
  stat_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(1:7)) +
  labs(x = "Curiosity rating", y = "Mean corrected hit rate") 
```


